word-cloud

### 2016-08-06 eda/word-cloud.Rmd
function

red <- c("salmon1", "tomato2", "orangered3", "red3", "firebrick4")
word_cloud(one$word, one$n, red)
green <- c("chartreuse2", "mediumseagreen", "forestgreen", 
           "seagreen", "darkgreen")
word_cloud(five$word, five$n, green)
```

>>>>

red <- c("salmon1", "tomato2", "orangered3", "red3", "firebrick4")
WordCloud(one$word, one$n, red)
green <- c("chartreuse2", "mediumseagreen", "forestgreen", 
           "seagreen", "darkgreen")
WordCloud(five$word, five$n, green)
```
